---
title: "Homework #1"
author: "Lynn Chen"
output: github_document
---

```{r setup}
library(tidyverse)
```

## Problem 1:

This code junk will create:

* a random sample of size 10 from a standard Normal distribution.
* a logical vector indicating whether elements of the sample are greater than 0. 
* a character vector of length 10
* a factor vector of length 10, with 3 different factor “levels”

```{r}
set.seed(1234)

problem1_df = 
  tibble(
    rand_sample = rnorm(10),
    sample_greater_than_0 = rand_sample > 0,
    char_vector = c("My", "name", "is", "Lynn", "A", "B", "C", "D", "E", "F"),
    factor_vector = factor(c("Low", "Medium", "High", "High", "Low", "High", "Medium", "Low", "Low", "Medium"))
  )
```

Take the mean of each variable in my data frame.

```{r mean pull }
mean(pull(problem1_df, rand_sample))
mean(pull(problem1_df, sample_greater_than_0))
mean(pull(problem1_df, char_vector))
mean(pull(problem1_df, factor_vector))
```

Able to take the mean of numbers and logical variables, but not the character and factor vectors. 


